Project-II by Group MexicoCity

### 2014-12-14 Project 2/report/paper.tex
report final update

\subsection{Collaborative-filtering}
Let $UA$ (users-artists) be equal to $Y_train$. We split the data into a training set $ua_{tr}$ and a test set $ua_{te}$. The values inside the matrix are the number of time an user heard an artist. One of the principle features of the problem now is to say whether a user “likes” an artist of not, and ideally to know how much.

@@

\section{Summary}
For people detection, we decided to opt for NN with the cross-validated parameters instead of the otherwise best-TPR simple SVM method. That is because we found the output of NN predictions to be more stable than that of SVM (score between -1 and 1, in contrast to usually off-interval output for SVM). The final parameters used are $L_2$ weight = $10^{-6}$, a dropout of 0.43 and dimensions of $[D 250 50 10 2]$, and using sigmood internally, we also increased the number of epochs to 40.
\subsubsection*{Acknowledgments}
We would like to thanks the teaching team for their availability during the exercise sessions and office hours but also on the forum. We also want to thanks Youssef who organized the milestone of the project.
\subsubsection*{References}
Kevin Murphy, Machine Learning : A Probabilistic Perspective {\em The MIT Press
Cambridge, Massachusetts
London, England,2012}\\
Trevor Hastie,Robert Tibshirani,Jerome Friedman : The Elements of
Statistical Learning. Data Mining,Inference,and Prediction. {\em Springer, 2008}\\
Gareth James,
Daniela Witten,
Trevor Hastie,
Robert Tibshirani:An Introduction to Statistical Learning.{\em Springer, 2013}
\end{document}

>>>>

\subsection{Collaborative-filtering}
Let $UA$ (users-artists) be equal to $Y_{train}$. We split the data into a training set $ua_{tr}$ and a test set $ua_{te}$. The values inside the matrix are the number of time an user heard an artist. One of the principle features of the problem now is to say whether a user “likes” an artist of not, and ideally to know how much.

@@

\section{Summary}
For people detection, we decided to opt for NN with the cross-validated parameters instead of the otherwise best-TPR simple SVM method. That is because we found the output of NN predictions to be more stable than that of SVM (score between -1 and 1, in contrast to usually off-interval output for SVM). The final parameters used are $L_2$ weight = $10^{-6}$, a dropout of 0.43 and dimensions of $[D \ 250 \ 50 \ 10 \  2]$, and using sigmood internally, we also increased the number of epochs to 40.\\

For the music recommender we managed to recommend songs successfully to existing users based on their similarity with other users. We predicted the counts using different models with sometimes good and very bad results. Our best was the model based on the similarity (collaborative-filtering) for the weak prediction. Some other model could have been tested if we had more time, for example clustering.
\subsubsection*{Acknowledgments}
We would like to thanks the teaching team for their availability during the exercise sessions and office hours but also on the forum. We also want to thanks Youssef who organized the milestone of the project.
\subsubsection*{References}
Kevin Murphy, Machine Learning : A Probabilistic Perspective {\em The MIT Press
Cambridge, Massachusetts
London, England,2012}\\
Trevor Hastie,Robert Tibshirani,Jerome Friedman : The Elements of
Statistical Learning. Data Mining,Inference,and Prediction. {\em Springer, 2008}\\
Gareth James,
Daniela Witten,
Trevor Hastie,
Robert Tibshirani:An Introduction to Statistical Learning.{\em Springer, 2013}
\end{document}
